Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-03-24 latex/comp_or.tex
Paper Comp OR update

\subsection{mpShims}

@@

\subsubsection{{\it Shims} first phase}

@@

\subsubsection{{\it Shims} second phase: improvement on minimizing CG deviation}
\label{subsection:second_phase}

Between the greedy and the {\it Shims} selection phases we inserted, in this work, an integer programming method to minimize the CG deviation, as stated by the model that follows.

@@

\subsubsection{{\it Shims} third phase}

@@

\subsection{3D packing}

We implemented a procedure for three-dimensional (3D) packing according to the instructions on \cite{DubeKanavathy2006}, on \cite{PaquaySchynsLimbourg2016}, and on \cite{PaquayLimbourgSchynsOliveira2018}, to pack the items selected for each pallet.

Our implementation was also based on \cite{RuizRibeiro}, taking advantage of the already implemented Python classes and auxiliary procedures, and the needed improvements to multi-core parallelism.

The heuristic solutions consider that, theoretically, all items selected for the pallets would fit on that pallet. But, due to the variability in item dimensions, an actual fit is not possible, causing some unfit items to be excluded from the previous heuristic's solutions (line \ref{3dpacking:unfit}).

Another important contribution is that we implemented parallel 3D packing with each pallet as a process.

@@

		\Procedure{$mp3Dpacking$}{${N^{\pi(k)}, \pi(k)}, limit, G$} \Comment{multi-processing 3D packing}

		\State Let $G(M^{\pi(k)},\ Q^{\pi(k)},\ E^{\pi(k)})$ \label{3dpacking:g1} \Comment{the initial solution}

		\For{$i \gets 1$ to $m$}
		\State $proc_i \gets 3Dpacker(p_i,\ N^{\pi(k)}_i,\ \pi(k),\ G )$   \label{3dpacking:greedy}
		\State $proc_i.start$
		\EndFor

		\For{$i \gets 1$ to $m$}
		\State $proc_i.join$   \Comment{wait for the packing process to finish.}
		\State $E^{\pi(k)}_i \gets E^{\pi(k)}_i \setminus proc_i.unfit$  \label{3dpacking:unfit} \Comment{exclude the unfit items from solution}
		\EndFor

		\Return $G(M^{\pi(k)},\ N^{\pi(k)} \cup Q^{\pi(k)},\ E^{\pi(k)})$ \label{3dpacking:return}

@@

@@

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}                       & $f$                &     10.34 &     8.50  &     12.42 &     15.06 &     15.97 &     15.88 &  0.96 \\% 7817
		&                                                & {\it run time (s)} &     < 1   &     3     &     5     &     20    &     58    &     352   &  1.0 \\% 439			
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}                     & $f$                &   12.96   &   7.53    &  12.28    &   13.20   &  13.71    &   13.44   &  0.90\\% 7278
		&                                                & {\it run time (s)} &     < 1   &     2     &     2     &     8    &     22    &     120   &  {\bf 2.8}\\%

@@

        \cmidrule{2-10}		                       
        &\multirow{2}{*}{ $Shims$}                       & $f$                &     14.68 &     12.21 &     17.67 &  21.01    &  22.64    &   21.91   &  0.96  \\%  11012
        &                                                & {\it run time (s)} &     < 1   &     2     &     3     &     12    &     33    &   209     &  1.0 \\% 260

        \cmidrule{2-10}		                       
        &\multirow{2}{*}{ $mpShims$}                     & $f$                &    16.12  &     11.81 &     17.48 &  17.66    &   19.81   &  17.61    &  0.87 \\% 9966
        &                                                & {\it run time (s)} &     < 1   &     1     &     2     &     7     &   20      &  120      &  {\bf 1.7}\\% 151

@@

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}                       & $f$                &    21.31  &  17.35    &   24.24   &   27.39    &  29.31     &  27.06     &   0.96  \\%  14666
		&                                                & {\it run time (s)} &     < 1   &     2     &     4     &     14     &     35     &   220     &  1.0 \\% 260

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}                     & $f$                &    24.33  &   17.26   &   24.70   &  24.81     &   27.71    &  24.93        &  0.94  \\% 14374
		&                                                & {\it run time (s)} &     < 1   &     2     &     3     &     9      &   26       &  151      &  {\bf 1.7}\\% 151

@@

\subsection{An attempt to minimize ground handling time}
\label{improvement}

\cite{LurkinSchyns2015} considered an aircraft with two doors, and the minimization of loading and unloading costs at the intermediate node was modeled through a container sequencing problem. But, as both aircrafts dealt with in this work have only the ramp door, we tried to minimize the distance of travel of pallets inside the cargo bay, favoring unloading in the next node, by a post optimization of pallets positions to favor this distance minimization.

So, to confirm or not Hypothesis (4), that the distances to move pallets on unloading in the next node could be minimized to benefit unloading costs. We modeled this improvement as follows.

@@

\vspace{2.0mm}
\begin{table}[!ht]
\centering
\caption{Distances minimization}  \label{tab:ground}
\footnotesize
%\scriptsize
\begin{tabular}{cc S[table-format=-1.1] S[table-format=-1.1] S[table-format=-1.3]}
\toprule
{\bf Volume}            &                & {\bf Before} & {\bf After} & {\bf Improvement} \\
{\bf Surplus}           & {\bf Scenario} & {\bf (m)}    & {\bf (m)}   & {\bf (\%)} \\		
\midrule
\multirow{6}{*}{ $1.2$} & $1$ &  31.0 &  29.0 & -5.9 \\
                        & $2$ & 189.7 & 189.4 & -0.4 \\
                        & $3$ & 152.0 & 152.0 & 0.0 \\
                        & $4$ & 134.0 & 130.7 & -2.4 \\ 
                        & $5$ & 115.7 & 115.7 & 0.0\\    
                        & $6$ &  &  & 0.0\\                                                                  
\midrule
\multirow{6}{*}{ $1.5$} & $1$ &  .0 &  .0 & 5.9 \\
						& $2$ & .7 & .4 & 0.4 \\
						& $3$ & .0 & .0 & 0.0 \\
						& $4$ & .0 & .7 & 2.4 \\ 
						& $5$ & .7 & .7 & 0.0\\    
						& $6$ &  &  & 0.0\\                                                                  
\midrule
\multirow{6}{*}{ $2.0$} & $1$ &  .0 &  .0 & 5.9 \\
						& $2$ & .7 & .4 & 0.4 \\
						& $3$ & .0 & .0 & 0.0 \\
						& $4$ & .0 & .7 & 2.4 \\ 
						& $5$ & .7 & .7 & 0.0\\    
						& $6$ &  &  & 0.0\\

\bottomrule
\end{tabular}
\end{table}

@@

(3) The procedure for 3-D packing generated an unfit item percentage of approximately 20\%. This solution phase was a parallel 3-D packing with each pallet as a process, which decreased this phase's run time by approximate a $n-1$ factor where $n$ is the number of pallets. This was possible because each packing process is completely independent; there is no multiprocessing shared memory. It is also important to highlight that, after the items were excluded, the CG deviation was kept within its operational and feasible range.

>>>>

@@

\subsubsection{{\it mpShims} first phase}

@@

\subsubsection{{\it mpShims} second phase}
\label{subsection:second_phase}

Between the greedy and the {\it Shims} selection phases we inserted, in this work, an integer programming method to minimize the CG deviation, as stated by the integer programming model that follows.

@@

\subsubsection{{\it mpShims} third phase}

@@

\subsection{Multiprocessing 3D packing}

According to \cite{BrandtStefan2019}, {\it Technically the task to solve is a three-dimensional Container Loading Problem (CLP) with a multitude of constraints. The CLP alone is known to be NP-hard and extremely hard to solve even for instances of moderate size. The typical number of items per transport segment ranges between 300 and 800 items.}

So, to confirm or not Hypothesis (3), we decided to adopt the model for three-dimensional (3D) packing based in the instructions on \cite{DubeKanavathy2006}, \cite{li2014} and on \cite{PaquayLimbourgSchynsOliveira2018}, to pack the items selected for each pallet.

The main logic of the 3D packing procedure is based on an approximate algorithm like follows:

From a list of items, items are sorted from the biggest to the smallest and placed in such an order on a pallet.Each item has 1 to 6 orientations to choose from when it can be placed. The orientation procedure can select the best direction type among possible orientations.

A pivot point is used to determine item's position. The pivot is an (x, y, z) coordinate which represents a point in the pallet at which an attempt to pack an item will be made.

The back lower left corner of the item will be placed at the pivot. If the item cannot be packed at the pivot position then it is rotated until it can be packed at the pivot point or until we have tried all 6 possible rotation types.

If, after rotating it, the item still cannot be packed at the pivot point, then we move on to packing another item and add the unpacked item to a list of items that will be packed after an attempt to pack the remaining items is made.

The first pivot in the empty pallet is always (0,0,0). When one item can be placed into multiple optimal pivot point, the placement selection module can help make a choice.

Let $n$ be the number of items and $m$ the number of pallets.

Let $A_{j}\ =\ 1$ if item $j$ is assigned to the pallet, $A_{j}\ =\ 0$ otherwise, for $j \in \{1,\ 2,\ 3,\ ...,\ n\}$.

Let $X_{ij}\ =\ 1$ if item $j$ was already assigned to pallet $i$ by {\it mpShims}, $X_{ij}\ =\ 0$ otherwise, for $i \in \{1,\ 2,\ 3,\ ...,\ m\}$.

Let $d_j,\ w_j,\ h_j$ be parameters indicating the depth, width, and height of an item. 
Let $D_i,\ W_i,\ H_i$ be parameters indicating the depth, width, and height of the pallet.

Let $x_j,\ y_j,\ z_j$ be real type variables for coordinates of item's left-bottom-behind corner.

Let $o_j^1,\ o_j^2,\ o_j^3,\ o_j^4,\ o_j^5,\ o_j^6$ be binary variables, indicating the possible orientations for item $j$. One of the values equal to 1 if item $j$ has orientation in $\{1,\ 2,\ 3,\ 4,\ 5,\ 6\}$, respectively, otherwise equal to 0.

\begin{equation} \label{eq:3dpacking1}
	\mbox{minimize} \Big [ D_i \times W_i \times H_i - \sum_{j \gets 1}^{n} X_{ij} \times A_{j} \times d_j \times w_j \times h_j \Big ]
\end{equation}

\begin{equation} \label{eq:3dpacking2}
	\sum_{j \gets 1}^{n} A_{j} \times d_j  \leq X_{ij} \times D_i,\ i \in \{1,\ 2,\ 3,\ ...,\ m\}
\end{equation}

\begin{equation} \label{eq:3dpacking3}
	\sum_{j \gets 1}^{n} A_{j} \times w_j  \leq X_{ij} \times W_i,\ i \in \{1,\ 2,\ 3,\ ...,\ m\}
\end{equation}

\begin{equation} \label{eq:3dpacking4}
	\sum_{j \gets 1}^{n} A_{j} \times h_j  \leq X_{ij} \times H_i,\ i \in \{1,\ 2,\ 3,\ ...,\ m\}
\end{equation}

Algorithm \ref{alg:3dpacking} presents the multiprocessing solution method for 3D packing to be applied after {\it mpShims}, to guarantee that the item to be palletized actually fit into the pallet.

@@

		\Procedure{$mp3Dpacking$}{${\pi(k)},\ G$}

		\State Let $G(M^{\pi(k)},\ N^{\pi(k)} \cup Q^{\pi(k)},\ E^{\pi(k)})$ \label{3dpacking:1}

		\State $proc \gets \{p_1,p_2,..., p_m\}$ \label{3dpacking:2}

		\For{$i \gets 1$ to $m$}
		\State $proc_i \gets 3Dpacker(p_i,\ N^{\pi(k)}_i,\ \pi(k),\ G )$   \label{3dpacking:3}
		\State $proc_i.start$
		\EndFor

		\For{$i \gets 1$ to $m$}
		\State $proc_i.join$ \label{3dpacking:4}
		\State $E^{\pi(k)}_i \gets E^{\pi(k)}_i \setminus proc_i.unfit$  \label{3dpacking:5} 
		\EndFor

		\Return $G(M^{\pi(k)},\ N^{\pi(k)} \cup Q^{\pi(k)},\ E^{\pi(k)})$

@@

According to line \ref{3dpacking:1}, this method receives an initial solution produced by {\it mpShims}, and according to line \ref{3dpacking:2}, each pallet has its own process.

In line \ref{3dpacking:3}, $N^{\pi(k)}_i$ is the set of items previously assigned to pallet $i$.

In line \ref{3dpacking:4}, the algorithm waits for the packing process to finish.

Line \ref{3dpacking:5} excludes the unfit items from solution.

\subsection{Minimization of the distance of a next node destined pallet to the ramp door }

\cite{LurkinSchyns2015} considered an aircraft with two doors, and the minimization of loading and unloading costs at the intermediate node was modeled through a container sequencing problem. But, as both aircraft dealt with in this work have only the ramp door, we tried to minimize the distance of travel of pallets inside the cargo bay, favoring unloading in the next node, by a post optimization of pallets positions to favor this distance minimization.

So, to confirm or not Hypothesis (4), that the distances to move pallets on unloading in the next node could be minimized to benefit unloading costs. We modeled this improvement as an integer programming model.

@@

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}                       & $f$                &     10.34 &     8.50  &     12.42 &     15.06 &     15.97 &     15.88 &  0.96 \\% 7817
		&                                                & {\it run time (s)} &     < 1   &     3     &     5     &     20    &     58    &     352   &  1.00 \\% 439			
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}                     & $f$                &   12.96   &   7.53    &  12.28    &   13.20   &  13.71    &   13.44   &  0.90\\% 7278
		&                                                & {\it run time (s)} &     < 1   &     2     &     2     &     8    &     22    &     120   &  {\bf 2.80}\\%

@@

        \cmidrule{2-10}		                       
        &\multirow{2}{*}{ $Shims$}                       & $f$                &     14.68 &     12.21 &     17.67 &  21.01    &  22.64    &   21.91   &  0.96  \\%  11012
        &                                                & {\it run time (s)} &     < 1   &     2     &     3     &     12    &     33    &   209     &  1.00 \\% 260

        \cmidrule{2-10}		                       
        &\multirow{2}{*}{ $mpShims$}                     & $f$                &    16.12  &     11.81 &     17.48 &  17.66    &   19.81   &  17.61    &  0.87 \\% 9966
        &                                                & {\it run time (s)} &     < 1   &     1     &     2     &     7     &   20      &  120      &  {\bf 1.70}\\% 151

@@

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}                       & $f$                &    21.31  &  17.35    &   24.24   &   27.39    &  29.31     &  27.06     &   0.96  \\%  14666
		&                                                & {\it run time (s)} &     < 1   &     2     &     4     &     14     &     35     &   220     &  1.00 \\% 260

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}                     & $f$                &    24.33  &   17.26   &   24.70   &  24.81     &   27.71    &  24.93        &  0.94  \\% 14374
		&                                                & {\it run time (s)} &     < 1   &     2     &     3     &     9      &   26       &  151      &  {\bf 1.70}\\% 151

@@

\subsection{Results of the 3D packing}

%\begin{table}[!h]
%	\begin{minipage}{0.5\linewidth}
%		left
%	\end{minipage}\hfill % these two lines must be close to each other
%	\begin{minipage}{0.5\linewidth}
%		right		
%	\end{minipage}
%\end{table}

\vspace{2.0mm}
\begin{table}[!ht]
\centering
\caption{Parallel 3D packing time increment}  \label{tab:3d}
\scriptsize
\begin{tabular}{c S[table-format=-1.1] S[table-format=-1.1] S[table-format=-1.1]}
\toprule
&   \multicolumn{3}{c}{\bf Average tour time - 3D packing}  \\
\cmidrule{2-4}
& {\bf without} & {\bf with} & {\bf increment} \\
{\bf Scenario} & {\bf (s)}    & {\bf (s)}   & {\bf (times)} \\		
\midrule
$1$ &   1 &   15 & 15 \\
$2$ &   5 &   76 & 15 \\
$3$ &   8 &   97 & 12 \\
$4$ &  35 &  330 &  9 \\ 
$5$ &  98 &  740 &  8 \\    
$6$ & 220 & 1500 &  7 \\                                                                  
\bottomrule
\end{tabular}
\end{table}

According to Table \ref{tab:3d}, the time increase with the 3D packing inclusion was approximately 10 times. About 40 min to solve a complete tour, against 4 min without the 3D packing procedure, considering the worst (6) scenario.
i.e., with the 3D packing procedure running in multiprocessing mode, this complete solution method for {\it ACLP+RPDP} is still viable for operational use.

\subsection{Results of the minimization of the pallet handling distances in the cargo bay}
\label{improvement}

@@

\vspace{2.0mm}
\begin{table}[!ht]
\centering
\caption{Average distances minimization}  \label{tab:ground}
%\footnotesize
\scriptsize
\begin{tabular}{c S[table-format=-1.1] S[table-format=-1.1] S[table-format=-1.3]}
\toprule
& {\bf Before} & {\bf After} & {\bf Improvement} \\
{\bf Scenario} & {\bf (m)}    & {\bf (m)}   & {\bf (\%)} \\		
\midrule
$1$ &  32.7 & 28.7 & -12.3 \\
$2$ & 193.3 & 188.9 & -2.3 \\
$3$ & 152.0 & 152.0 &  0.0 \\
$4$ & 134.0 & 130.7 & -2.4 \\ 
$5$ & 118.0 & 116.1 & -1.6 \\    
$6$ & 106.0 & 104.1 & -1.8 \\                                                                  
\bottomrule
\end{tabular}
\end{table}

@@

(3) The procedure for 3-D packing generated an unfit item percentage of approximately 17\%, in average. 
We are conscious that this unfit rate could be smaller if we had chosen \cite{PaquaySchynsLimbourg2016} or \cite{PaquayLimbourgSchynsOliveira2018} approaches, but as we are concerned with an operational application where the running time is crucial, we stick to an approximate approach.

{\it mpShims} consider that, theoretically, all items selected for the pallets would fit. But, due to the variability in item dimensions, an actual complete fit is not possible, causing some unfit items to be excluded from the previous solution (line \ref{3dpacking:unfit}).

This solution phase was a parallel 3-D packing with each pallet as a process, which decreased this phase's run time by approximate a $n-1$ factor where $n$ is the number of processes. This was possible because each packing process is completely independent; there is no multiprocessing shared memory. It is also important to highlight that, after the items were excluded, the CG deviation was kept within its operational and feasible range.
